Project Light

### 2015-08-28 paper/paper.tex
add sig-alternate class and use it in paper
add related work section and add paper from Konrads mail
fix authors - no empty lines allowed
better style for authors mail

% v2-acmtog-sample.tex, dated March 7 2012
% This is a sample file for ACM Transactions on Graphics
%
% Compilation using 'acmtog.cls' - version 1.2 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.2 - March 2012
\documentclass{acmtog} % V1.2

%\acmVolume{VV}
%\acmNumber{N}
%\acmYear{YYYY}
%\acmMonth{Month}
%\acmArticleNum{XXX}
%\acmdoi{10.1145/XXXXXXX.YYYYYYY}

\acmVolume{VV}
\acmNumber{XX}
\acmYear{2015}
\acmMonth{August}
\acmArticleNum{XX}
\acmdoi{10.1145/1559755.1559763}

@@

\author{
	Cornelius Bock, Konrad-Felix Krentz, Daniel Werner, Felix Wolff
}

@@

>>>>

% v2-acmtog-sample.tex, dated March 7 2012
% This is a sample file for ACM Transactions on Graphics
%
% Compilation using 'acmtog.cls' - version 1.2 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.2 - March 2012
\documentclass{sig-alternate} % v 2.5

% --- Author Metadata here ---
\conferenceinfo{Sample Conferenve}{'15 Potsdam, Germany}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{5}

\author{
\alignauthor
Cornelius Bock
%
\alignauthor
Daniel Werner
%
\alignauthor
Felix Wolff
%
\and
\texttt{\{cornelius.bock|daniel.werner|felix.wolff\}@student.hpi.de} \\ \\
\and
\alignauthor
Christoph Meinel\\
    \affaddr{\textit{Supervisior}}
%
\alignauthor
Konrad-Felix Krentz\\
    \affaddr{\textit{Supervisior}}
}

\category{K.6.5}{Management Of Computing And Information Systems}{Security}

@@

\section{Related Work}
\label{sec:related_work}

\begin{itemize}
	\item LiDSN: A Method to Deploy Wireless Sensor Networks Securely based on light communication
	\item ...
\end{itemize}
